PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-29 paper/paper.tex
Pattern discovery description added

>>>>

\subsection{Pattern Discovery}

This task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
Given the novelty of this task \footnote{The first year to appear on MIREX was 2013.}, the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX\cite{Collins2013}, which resulted in 19 different scores, each one (except for the two that evaluate the algorithm execution time) implemented in MIR-eval and described below:

\begin{itemize}
    \item
      \textbf{Standard F-measure, Precision, and Recall (F$_1$, P, R)}: This metric, composed of three scores, checks if the prototype patterns of the reference match possible key-transposed patterns in the prototype patterns of the estimations.
      Since the sizes of these prototypes must be equal, this metric is quite restrictive and it tends to be 0 most of the time (see 2013 MIREX results).
    \item
      \textbf{Establishment F-measure, Precision, and Recall (F1$_{est}$, P$_{est}$, R$_{est}$)}: These scores evaluate the amount of patterns that were successfully identified by the estimated results, no matter how many occurrences they found.
      In other words, this metric captures the ability of the algorithm to \textit{establish} that the estimated patterns are actually contained in the reference annotation.
    \item 
      \textbf{Occurrence F-measure, Precision, and Recall (F1$_{occ}$, P$_{occ}$, R$_{occ}$)}: Independently of how many patterns were correctly established, we may also want to know how well the algorithm finds all their respective occurrences throughout the piece.
      This metric aims to quantize this \textit{occurrence} retrieval quality of the algorithm.
      This metric has a tolerance parameter $c$ to allow differences when evaluating the similarity between occurrences, and in MIREX they use $c=.75$ and $c=.5$.
    \item
      \textbf{Three-layer F-measure, Precision, and Recall (TLF$_1$, P$_3$, R$_3$)}: These scores can be seen as an improved version of the standard metrics.
      They capture both the establishment of the patterns and the occurrence retrieval in a single set of scores, being more permissive than the standard evaluation.
    \item
      \textbf{First $N$ patterns metrics (FFTP$_{est}$, FFP)}: This includes the first $N$ patterns target proportion establishment recall, and the first $N$ patterns three-layer precision. 
      By analyzing the first $N$ patterns only, we evaluate the ability of the algorithm of sorting the identified patterns based on their relevance. 
      In MIREX, $N=5$.

\end{itemize}
